### 2012-06-29 docs/architecture/architecture.tex
add note about new EOS interface

The {\tt eos\_module} declares for convenience the variables that need
appear in the {\tt eos} call argument list.  \maestro\ routines use
these module variables in the EOS call to avoid having to declare 
each quantity in each routine that calls the EOS.

>>>>

The thermodynamic quantities are stored in a Fortran type {\tt eos\_t},
which has fields for all the thermodynamic inputs and outputs.  The 
type definition is brought in through {\tt eos\_type\_module}.
\footnote{ Note: an older interface to the EOS exists, but is
  deprecated.  In this mode, the {\tt eos\_module} declares for
  convenience the variables that need appear in the {\tt eos} call
  argument list.  \maestro\ routines use these module variables in the
  EOS call to avoid having to declare each quantity in each routine
  that calls the EOS.}
